The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2017-09-04 JStatSoft_forestinventory_master.rnw
update Andreas 31.08.2017(2)
some changes

%% an abstract and keywords
\Abstract{
Forest inventories provide reliable and evidence-based information to assess the state and development of forests over time.  They typically consist of a random sample of plot locations in the forest that are assessed individually by hand. Due to the high costs of these terrestrial campaigns, remote sensing information available in high quantity and low costs (e.g. LiDAR, stereophotogrammetry, etc.) is frequently incorporated in the estimation process in order to reduce inventory costs or improve estimation precision. With respect to this objective, the application of \textit{multiphase} forest inventory methods (e.g. double- and triple-sampling regression estimators) has proved to be efficient. While these methods have been successfully applied in practice, the availability of open-source software has been rare if not non-existent. The \proglang{R} package \pkg{forestinventory} provides a comprehensive set of global and small area regression estimators for multiphase forest inventories under simple and cluster sampling. The implemented methods have been demonstrated in various scientific studies ranging from small to large scale forest inventories, and can be used for post-stratification, regression and regression within strata. This article summarizes the mathematical theory of this family of design-based estimators and demostrates how they can be easily implemented in \proglang{R}.}

>>>>

%% an abstract and keywords
\Abstract{
Forest inventories provide reliable and evidence-based information to assess the state and development of forests over time.  They typically consist of a random sample of plot locations in the forest that are assessed individually by hand. Due to the high costs of these terrestrial campaigns, remote sensing information available in high quantity and low costs (e.g. LiDAR, stereophotogrammetry, etc.) is frequently incorporated in the estimation process in order to reduce inventory costs or improve estimation precision. With respect to this objective, the application of \textit{multiphase} forest inventory methods (e.g. double- and triple-sampling regression estimators) has proved to be efficient. While these methods have been successfully applied in practice, the availability of open-source software has been rare if not non-existent. The \proglang{R} package \pkg{forestinventory} provides a comprehensive set of global and small area regression estimators for multiphase forest inventories under simple and cluster sampling. The implemented methods have been demonstrated in various scientific studies ranging from small to large scale forest inventories, and can be used for post-stratification, regression and regression within strata. This article summarizes the mathematical theory of this family of design-based estimators and demonstrates how they can be easily implemented in \proglang{R}.}

### 2017-09-04 rnw/Main structure and modules of the Package.Rnw
update Andreas .4.09.2017(1)
update Andreas 04.09.2017(3)
some changes

The selection of a suitable predictive model is an essential part in the application of multiphase inventories.  If the model is chosen poorly it could lead to inefficient use of the auxiliary information or even biased estimates.  This brings us to the two schools of thought concerning estimation: \textit{model-dependent} (also known as \textit{model-based}) and design-based. In the \textit{model-dependent} framework, the sample locations \textit{x} are fixed and the observation $Y(x)$ taken at location $x$ is assumed to be a random variable as the realization of a stochastic process. The model does not need to be fit from a probability sample, but it does need to be trusted in the sense that all of its model assumptions need to be verified.  For example, if we select a linear model using OLS then there is an implicit mathematical assumption that the residuals are \textit{iid}.  This model assumption needs to be empirically verified in order to avoid misinterpreting the regression coefficients and even the predictions. The unbiasedness of model-dependent estimators depend on the correct specification of the model, which means that extensive analyses and adjustments must be conducted to ensure that the model adequately describes the underlying stochastic process. In contrast, the \textit{design-based} (also called \textit{model-assisted}) approach rests upon the randomization of the sample locations $x$. At any given location $x_0$, the ground truth, $Y(x_0)$, is assumed to be fixed and \textit{not} the result of a stochastic process.  $Y(x)$ is random only because of the random selection of the plot locations $x$.  but the selection of     forest itself is fixed . The observation \textit{Y}(\textit{x}) itself still remains a random variable, but solemnly due to the random sample mechanism. A consequence of this approach is that the regression models used in the design-based regression estimators do no longer have to satisfy any model assumptions in the classical statistical sense (e.g. identical distribution and independence of the observation $Y(x)$, or stationarity assumption in the geostatistical frame), as it is the case in the model-based framework \cite{mandallaz2008}. The philosophy of the design-based approach is thus to use prediction models to \textit{improve} the efficiency of the estimators without having to \textit{rely} on their correct specification, which makes them very attractive to be used in official statistics. They are therefore also referred to as \textit{model-assisted}. The randomly distribution of the sample locations, which the design-based inference rests upon, is in practice often replaced by the use of systematic grids due to minimization of travelling cost in the terrestrial survey. However, there is reasonable and empirical evidence that softening this assumption is acceptable for point estimation as well as the variance estimation, which will in most cases by slightly overestimated \citep{mandallaz2008, mandallaz2016}.

>>>>

The selection of a suitable predictive model is an essential part in the application of multiphase inventories.  If the model is chosen poorly it could lead to inefficient use of the auxiliary information or even biased estimates.  This brings us to the two schools of thought concerning estimation: \textit{model-dependent} (also known as \textit{model-based}) and design-based. In the \textit{model-dependent} framework, the sample locations \textit{x} are fixed and the observation $Y(x)$ taken at location $x$ is assumed to be a random variable as the realization of a stochastic process. The model does not need to be fit from a probability sample, but it does need to be trusted in the sense that all of its model assumptions need to be verified.  For example, if we select a linear model using OLS then there is an implicit mathematical assumption that the residuals are \textit{iid}.  This model assumption needs to be empirically verified in order to avoid misinterpreting the regression coefficients and even the predictions. The unbiasedness of model-dependent estimators depend on the correct specification of the model, which means that extensive analyses and adjustments must be conducted to ensure that the model adequately describes the underlying stochastic process. In contrast, the \textit{design-based} (also called \textit{model-assisted}) approach rests upon the randomization of the sample locations $x$. At any given location $x_0$, the ground truth, $Y(x_0)$, is assumed to be fixed and \textit{not} the result of a stochastic process.  $Y(x)$ is random only because of the random selection of the plot locations $x$, which is determined by the sampling design.  A consequence of this approach is that the models used in the design-based regression estimators do no longer have to satisfy any model assumptions in the classical statistical sense (e.g. identical distribution and independence of the observation $Y(x)$, or stationarity assumption in the geostatistical frame), as it is the case in the model-based framework \cite{mandallaz2008}. The philosophy of the design-based approach is thus to use prediction models to \textit{improve} the efficiency of the estimators without having to \textit{rely} on their correct specification, which makes them very attractive to be used in official statistics. They are therefore also referred to as \textit{model-assisted}. The randomly distribution of the sample locations, which the design-based inference rests upon, is in practice often replaced by the use of systematic grids due to minimization of travelling cost in the terrestrial survey. However, there is reasonable and empirical evidence that softening this assumption is acceptable for point estimation as well as the variance estimation, which will in most cases by slightly overestimated \citep{mandallaz2008, mandallaz2016}.
